Simulations (mix normal prior), ctwas_rss, 45k samples

### 2021-05-09 analysis/index.Rmd
added smr-heidi results, scripts matching v0.1.25

* [**Using UKbiobank data (22k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s40.22.html)

@@

* [**Using UKbiobank data (45k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s80.45.html)

@@

* [**Using UKbiobank data (22k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s40.22_mixnormal.html)

* [**Using UKbiobank data (45k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s80.45_mixnormal.html)

>>>>

* [**Using UKbiobank data (22k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s40.22_041521.html)

@@

* [**Using UKbiobank data (45k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s80.45_041621.html)

@@

* [**Using UKbiobank data (22k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s40.22_mixnormal_041721.html)

* [**Using UKbiobank data (45k samples), fusion weights Adipose**](simulation-ctwas-ukbWG-gtex.adipose_s80.45_mixnormal_041821.html)

### 2021-05-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22_041521.Rmd
added smr-heidi results, scripts matching v0.1.25

```{r libs}
library(ctwas)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source('~/causalTWAS/causal-TWAS/analysis/summarize_twas-coloc_plots.R')
source('~/causalTWAS/causal-TWAS/code/qqplot.R')
```

@@

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
```

>>>>

```{r libs}
library(ctwas)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source('~/causalTWAS/causal-TWAS/analysis/summarize_twas-coloc_plots.R')
source('~/causalTWAS/causal-TWAS/analysis/summarize_focus_plots.R')
source('~/causalTWAS/causal-TWAS/analysis/summarize_smr_plots.R')
source('~/causalTWAS/causal-TWAS/code/qqplot.R')
```

@@

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
We ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}

plot_focus <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    focusfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous.focus.tsv")

    f1 <- califocusPIP_plot(phenofs, focusfs)
    f2 <- ncausalfocusPIP_plot(phenofs, focusfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
}

plot_smr <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    smrfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous.smr")

    f1 <- caliSMRp_plot(phenofs, smrfs)
    f2 <- ncausalSMRp_plot(phenofs, smrfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
}
```

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```

### 2021-05-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22_mixnormal_041721.Rmd
added smr-heidi results, scripts matching v0.1.25

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415_compare/"
runtag = "ukb-s40.22-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

### ctwas

@@

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
We ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}

plot_focus <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    focusfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous.focus.tsv")

@@

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

>>>>

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210417/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210417_compare/"
runtag = "ukb-s40.22-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

@@

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
we ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, "ukb-s40.22-adi", "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)

}
plot_focus <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    focusfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous.focus.tsv")

@@

simutags <- paste(2, c(1,3:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

### 2021-05-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_041621.Rmd
added smr-heidi results, scripts matching v0.1.25

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415_compare/"
runtag = "ukb-s40.22-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

Results: Each row shows parameter estimation results from 5 simulation runs with similar settings (i.e. pi1 and PVE for genes and SNPs). Results from each run were represented by one dot, dots with the same color come from the same run. `truth`: the true parameters,  `selected_truth`: the truth in selected regions that were used to estimate parameters, `ctwas`: ctwas estimated parameters (using summary statistics as input).

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
We ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

configtag <- 1
runtag = "ukb-s40.22-adi"

@@

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

@@

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```

>>>>

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210418/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210418_compare/"
runtag = "ukb-s80.45-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

Results: Each row shows parameter estimation results from 5 simulation runs with similar settings (i.e. pi1 and PVE for genes and SNPs). Results from each run were represented by one dot, dots with the same color come from the same run. `truth`: the true parameters,  `selected_truth`: the truth in selected regions that were used to estimate parameters, `ctwas`: ctwas estimated parameters (using summary statistics as input). 
We run FUSION following default settings and adjust p values by BH method to get expected FDP. 
We ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, "ukb-s80.45-adi", "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

configtag <- 1
runtag = "ukb-s80.45-adi"

@@

simutags <- paste(5, c(1, 3:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

@@

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

```

### 2021-05-09 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_mixnormal_041821.Rmd
added smr-heidi results, scripts matching v0.1.25

---
title: "Simulations to test ctwas summary stats version, 45k samples"
output: html_document
---

@@

# `ctwas` results

Results: Each row shows parameter estimation results from 5 simulation runs with similar settings (i.e. pi1 and PVE for genes and SNPs). Results from each run were represented by one dot, dots with the same color come from the same run. `truth`: the true parameters,  `selected_truth`: the truth in selected regions that were used to estimate parameters, `ctwas`: ctwas estimated parameters (using summary statistics as input). 
We run FUSION following default settings and adjust p values by BH method to get expected FDP. 
We ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

@@

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

```

>>>>

---
title: "Simulations (mix normal prior), ctwas_rss, 45k samples"
output: html_document
---

@@

# `ctwas` results + other comparators

Results: Each row shows parameter estimation results from 5 simulation runs with similar settings (i.e. pi1 and PVE for genes and SNPs). Results from each run were represented by one dot, dots with the same color come from the same run. `truth`: the true parameters,  `selected_truth`: the truth in selected regions that were used to estimate parameters, `ctwas`: ctwas estimated parameters (using summary statistics as input).

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
we ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).
We ran SMR+HEIDI, using eQTL summary statistics GTEx v.7. We filter the results by requiring p_HEIDI > 0.05. The plots 
are based on SMR p value adjusted by BH method to get expected FDP.

@@

simutags <- paste(2, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

@@

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```
